*Prochlorococcus marinus* responses to light and oxygen

### 2024-05-28 Code/Manuscript_O2.Rmd
added niche map

```{r read temperate niche sheet, include=FALSE}

ProchloroNiches <- read_csv(file.path(DataIn, "Prochlorococcus_temperate_niches.csv"))

ProchloroNiches <- ProchloroNiches %>% 
  mutate(MED4 = case_when(MED4 == "Potential" ~ "+",
                          MED4 == "Excluded" ~ "-"),
         SS120 = case_when(SS120 == "Potential" ~ "+",
                          SS120 == "Excluded" ~ "-"),
         MIT9313 = case_when(MIT9313 == "Potential" ~ "+",
                          MIT9313 == "Excluded" ~ "-"))

@@

```{r NichesTable,  fig.height = 8, fig.width = 6, echo = FALSE}

knitr::kable(ProchloroNiches,
             caption = "Potential temperate niches for *Prochlorococcus marinus* ecotypes defined by season, depth, and oxygen; Full denotes 250 µM of dissolved oxygen and OMZ denotes 25 µM of dissolved oxygen. Plus symbols (+) indicate a potential niche, minus symbols (-) not a potential niche.",
        align = "lllccc" )
```

>>>>

```{r NichesMap, fig.cap = NichesMap_cap, fig.height = 15, fig.width = 15, echo = FALSE}

NichesMap_cap <- glue(" Figure caption for Potential Temperate Future Niche map goes here.",

knitr::include_graphics(file.path(FiguresIn, "MapComboPro.png"))

@@
